\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-09-02 paper.tex
WIP state of the art

\begin{itemize}
    \item FSM: SMACH
    \item agent-based approaches: ROAR
    \item logic languages: OpenPRS, CRAM
    \item dedicated control languages: URBI
    \item similar attempts: teer (co-routine: cooperative multi-threading)
    \item and the vast majority: ad-hoc scripts
\end{itemize}

@@

    robot.lift_box()
    robot.wave_hand() # waits until lift_box is over
    robot.scratch_head() # skipped

@@

    # {'x':0., 'y':0., 'z':0., 
    #  'qx':0., 'qy':0., 'qz':0., 'qw':1., 
    #  'frame': 'handL'}
    robot.poses["handL"]

    # {'x':1., 'y':0., 'z':0., 
    #  'qx':0., 'qy':0., 'qz':0., 'qw':1., 
    #  'frame': 'map'}
    robot.poses[(1.0, 0.0, 0.0)]

    # {'x':0., 'y':0., 'z':1., 
    #  'qx':0., 'qy':0., 'qz':0.0998, 'qw':0.0995, 
    #  'frame': 'handL'}
    robot.poses[{'z':1.0, 'rz':0.2, 'frame':'handL'}]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
\begin{center}
\begin{tabular}{p{0.9\columnwidth}}
\hline
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
\hline
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
\hline
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
\hline
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
\hline
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
\hline
\end{tabular}
\end{center}
\caption{Examples of \pyRobots actions, mostly stemming from experiments involving
    the PR2 robot.}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{cowriter}
        \caption{Children teaching An Aldebaran Nao interacting with }
        \label{expe-cowriter}
\end{figure}

@@

\section{Future Work}

\begin{itemize}
    \item control mixing policies?
    \item control over action priorities
\end{itemize}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,biblio}

>>>>

Any robotic experiment requires a certain amount of high-level control to
supervise the robot behaviour, and, expectedly, many projects have attempted to
design and provide tools for this task.  We focus this review on \emph{tools
dedicated to the explicit implementation of high-level behaviours}, excluding
complete control stacks (that would typically include a middleware and hardware
abstractions), meta-tools (like component generators or model checkers) and
(semi-)automatic techniques (like learning by demonstration).  In contrast with
middlewares for which the robotic community relies on a few \emph{de-facto}
standards (ROS, YARP, OpenRTM), we want to underline that no such widely-used
softwares exist for execution control, and we believe that most of today's robot
behaviours are implemented as \emph{ad-hoc} scripts.

We identify three categories of execution control tools: \emph{finite state
machines}, \emph{agent-based} controllers and
\emph{domain-specific languages} (DSL), including \emph{embedded domain-specific
languages} (eDSL,~\cite{joyeux2011robot}). These categories overlap to a certain
extend, but they should reasonably reflect the motivational concepts/ideas that
gave birth to the specific tools.

\paragraph{Finite State Machines} (or FSM) are the most well-known paradigm to
describe how a robot goes from one \emph{state} (typically, performing an
action) to another state when some condition becomes true or some event is
triggered. Common FSM implementations in robotics include {\sc
rfSM}~\cite{klotzbucher2010orocos} (part of the OROCOS framework) and
{\sc smach}~\cite{bohren2010smach}. State machine semantics are well
understood~\cite{harel1996statemate} and provide a well structured model,
suitable for meta-reasoning (like verification). However, FSM are also
acknowledged to be ill-suited for complex systems (where the number of state
easily ``explodes'') or relatively dynamic and unpredictable environments where
it can prove difficult to \textit{a priori} exhaustively list transitions.

\paragraph{Agent-based controllers}

temporal planning/temporal constraints: T-REX~\cite{mcgann2007trex} -> sensing-planning-acting

ROAR: ~\cite{degroote2011roar}

\paragraph{Domain-specific languages}

Domain-specific languages (DSL), in the widest sense, represent the largest body
of literature on high-level behaviour programming. They can either be ``actual''
domain-specific languages like PRS~\cite{ingrand1996prs},
RPL~\cite{mcdermott1993reactive}, Golog~\cite{levesque1997golog} (and its
derivative like {\sc ReadyLOG}~\cite{ferrein2007robot} or, more recently,
URBI~\cite{baillie2005urbi}; or what Joyeux calls \emph{embedded}
DSL~\cite{joyeux2011robot}: extensions of existing languages (typically, dynamic
languages like Python or Ruby, or logic languages like Prolog) to provide
high-level paradigms and control structures well suited to the programming of
robots. {\sc cram}~\cite{beetz2010cram} (based on Lisp and Prolog), {\sc
roby}~\cite{joyeux2009plan} (based on Ruby), {\sc
teer}~\footnote{\url{http://wiki.ros.org/executive_teer}} (based on Python), are
examples of such eDSL.

Projects like PRS, Golog or {\sc cram} have large scopes:

\pyRobots positions itself in this landscape as a lightweight eDSL (in a similar
fashion to {\sc roby} or {\sc teer}), that focuses on high-level behaviours
implementation. It seeks unobstrusive interaction with the other components of
the robot software stack, using Python as ubiquitous binding language. Similar
to URBI, it focuses on transparent preemptive concurrency and event-based programming.
Also, \pyRobots' model favours hierarchical task composition over plans, and does not
provide by itself any task planning service, delegating this to external tools.

@@

    robot.lift_box()
    robot.wave_hand() # waits until lift_box is over
    robot.scratch_head() # skipped if lift_box 
                         # is still running

@@

    robot.poses["handL"]
    # -> {'x':0., 'y':0., 'z':0., 
    #    'qx':0., 'qy':0., 'qz':0., 'qw':1., 
    #    'frame': 'handL'}

    robot.poses[(1.0, 0.0, 0.0)]
    # -> {'x':1., 'y':0., 'z':0., 
    #    'qx':0., 'qy':0., 'qz':0., 'qw':1., 
    #    'frame': 'map'}

    robot.poses[{'z':1.0, 'rz':0.2, 'frame':'handL'}]
    # -> {'x':0., 'y':0., 'z':1., 
    #    'qx':0., 'qy':0., 'qz':0.0998, 'qw':0.0995, 
    #    'frame': 'handL'}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
\begin{center}
\begin{tabular}{p{0.9\columnwidth}}
\hline
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
\hline
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
\hline
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
\hline
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
\hline
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
\hline
\end{tabular}
\end{center}
\caption{Examples of \pyRobots actions, mostly extracted from experiments involving
    the PR2 robot.}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{cowriter}
        \caption{Children teaching an Aldebaran Nao interacting how to
        handwrite.}
        \label{expe-cowriter}
\end{figure}

@@

\section{Conclusion and Future Work}

\subsection{Summary and main contributions}

\begin{itemize}
    \item strives to simplicity (from a user perspective)
    \item Middleware independent, real-world deployments with with ROS, GenoM, NAOqi, aseba
\end{itemize}

\subsection{Future work}

\begin{itemize}
    \item control mixing policies?
    \item control over action priorities
    \item path to more complex control tool (T-REX, etc)
\end{itemize}

@@

\bibliographystyle{IEEEtran}
\bibliography{pyrobots}
